Author's fourth reply to the referee report of \\ \textsc{ ``PERSISTENT HOMOLOGY FOR FUNCTIONALS'' }

### 2023-10-10 ref_reply4.tex
Fix typos found by referee (round 4)

\title{Author's fourth reply to the referee report of \\ \textsc{
		``PERSISTENT HOMOLOGY FOR FUNCTIONALS''
	}
}
\author{Bauer \and Medina-Mardones \and Schmahl}
\begin{document}
	\maketitle
	We want to thank the referee for once again reading our revised article very carefully and for taking the time to give us very helpful and detailed commentary throughout the review process going far beyond the usual scope of referee's reports.

	\section{First point}
	It was simply an oversight on our part to not include this condition. We have added it to the definition and also briefly expanded on why the restriction $G$ of $F$ in the proof of Lemma 5.13 is weakly upper-reducible if $F$ is.
	\section{Second point}
	The Eda--Kawamura result can indeed not be applied directly to the space $M$ since $M$ need not be compact. We have adapted the proof by applying the Eda--Kawamura result to each sublevel set of $F$ before passing to the colimits, which is still sufficient to reach our desired conclusion.
	\section{Third point}
	We have extended the proof of Lemma 5.11 (now Theorem 5.11) to fill the gaps left in Morse's work and make his line of reasoning using a ``related homotopy'' explicit. We promoted the statement to the status of a theorem, since the proof is quite extensive, and the statement itself is of general interest for Morse theory. 
	\section{List of typos, minor remarks and suggestions.}
	\begin{enumerate}
		\item Mentioning boundedness from below was indeed superfluous on page 26 because it follows from compactness of sublevel sets, we have removed the mention of the boundedness property.
		\item Changed as suggested.
		\item Changed as suggested.
		\item It should have indeed said ``disjoint'' instead of ``distinct''. We have also corrected this in the statement of Theorems 5.3 and 5.8.
		\item As suggested, we have distinguished the two cases where either $t_{1} \neq t_{2}$ or $t_{1} = t_{2}$.
		\item Changed as suggested.
		\item Weak upper-reducibility was indeed not needed here, we have removed the assumption.
		\item Changed as suggested.
		\item The mentioned part of the proof was indeed not quite accurate. We have implemented the suggested fix, where $q_{n}$ can be chosen such that $F(\varphi(q_{n},1)) \to t$ because of the assumption $t \geq F(\varphi(q,1)) > t - \epsilon$ that is supposed to lead to a contradiction.
		\item We changed the bounds of the interval accordingly.
		\item Changed as suggested.
		\item The entire argument has been rewritten, so some of the relevant quantities have changed. In particular, the cover by balls of radius $\delta/3$ has been changed to balls of radius $\delta/6$.
		\item Changed as suggested.
	\end{enumerate}

	\section{Other changes}
	\begin{enumerate}
		\item We have slightly changed the definition of displacement function in Definition 5.1. Before, we were paraphrasing the version by Struwe, but now we are more closely following the version by Morse--Tompkins, which requires a certain monotonicity. This actually makes the continuity assumption for displacement functions unnecessary. We have thus also removed the continuity assumption and have correspondingly removed the explanation for why we add this assumption from Remark 5.4. We have also correspondingly modified the end of the second paragraph of the proof of Lemma 5.11, where continuity of the displacement function has previously been used.
		\item We have changed the part of the proof of Lemma 5.11 where homotopies are extended from balls to the whole sublevel set insofar that we now describe the extension process before choosing a cover by finitely many balls. This removes the additional index $i$ in the description of the extension process, which improves readability.
	\end{enumerate}
\end{document}

>>>>

\title{Author's fourth reply to the referee report of \\ \textsc{
		``PERSISTENT HOMOLOGY FOR FUNCTIONALS''
	}
}
\author{Bauer \and Medina-Mardones \and Schmahl}
\begin{document}
	\maketitle

	\section*{Corrections}
	\begin{enumerate}
		\item Fixed.
		\item Fixed.
		\item ...
		\item Fixed.
		\item ...
		\item ...
		\item Fixed.
		\item ...
		\item ...
		\item Fixed
	\end{enumerate}
\end{document}

### 2023-10-10 sec/persistence.tex
Fix typos found by referee (round 4)

The most commonly used existence result for barcode decompositions is due to Crawley-Boevey \cite{Crawley-Boevey.2015}.
It guarantees the existence of a barcode decomposition for any \emph{pointwise finite dimensional} ($\PFD$) persistence module, which is a persistence modules $M$ such that $M_t$ is a finite dimensional vector space for all~$t \in \R$.
Unfortunately, the $\PFD$ condition is too restrictive for many purposes.
In particular, it is unsuited for the applications of Morse and Tompkins in minimal surface theory.
An appropriate weakening of $\PFD$ for more general settings is the notion of \emph{q-tameness}.
A persistence module $M$ is q-tame if the rank of the map $M_{s,t} \colon M_s \to M_t$ is finite for all $s < t$ \cite{Chazal.2016a}.
As exemplified by the infinite product of interval modules $\prod_{n \in \N_{> 0}} C([0,1/n))$, not every q-tame persistence module admits a barcode decomposition in the above sense.
Yet, there are multiple ways to regularize q-tame persistence modules in order to obtain invariants similar to barcodes \cite{Chazal.2016a, Chazal.2016b, Schmahl.2021}.
We briefly recall the approach from \cite{Chazal.2016b}.

>>>>

The most commonly used existence result for barcode decompositions is due to Crawley-Boevey \cite{Crawley-Boevey.2015}.
It guarantees the existence of a barcode decomposition for any \emph{pointwise finite dimensional} ($\PFD$) persistence module, which is a persistence module $M$ such that $M_t$ is a finite dimensional vector space for all~$t \in \R$.
Unfortunately, the $\PFD$ condition is too restrictive for many purposes.
In particular, it is unsuited for the applications of Morse and Tompkins in minimal surface theory.
An appropriate weakening of $\PFD$ for more general settings is the notion of \emph{q-tameness}.
A persistence module $M$ is q-tame if the rank of the map $M_{s,t} \colon M_s \to M_t$ is finite for all $s < t$ \cite{Chazal.2016a}.
As exemplified by the infinite product of interval modules $\prod_{n \in \N_{> 0}} C([0,1/n))$, not every q-tame persistence module admits a barcode decomposition in the above sense.
Yet, there are multiple ways to regularize q-tame persistence modules in order to obtain invariants similar to barcodes \cite{Chazal.2016a, Chazal.2016b, Schmahl.2021}.
We briefly recall the approach from \cite{Chazal.2016b}.

### 2023-10-10 sec/surfaces.tex
Fix typos found by referee (round 4)

\begin{rem}\label{rem:critical_set}
    %Our \cref{def:critical_set} of homotopically regular point differs slightly from that of \citet[p.~30]{Morse.1938} and \citet[p.~444--445]{Morse.1939} as their displacement functions are not explicitly assumed to be continuous.
    %As used in the proof of \cref{thm:sublevel_set_homotopy}, we require this property to establish that a homotopically regular point with value $t$ admits a neighborhood $U$ and a homotopy $\varphi$ as in \cref{def:critical_set} such that for any compact $V \subseteq U$ there is $\epsilon > 0$ with $\varphi(V, 1) \subseteq F_{\leq t - \epsilon}$.
    %That such neighborhoods exist is claimed by Morse in the proof of \cite[Lemma~8.1]{Morse.1938}, where continuity of the displacement functions is not mentioned explicitly.
    %It is not clear to us whether the claim actually holds without continuity, or whether the assumption of continuity was made implicitly.
    %Regardless, all displacement functions considered by \citet{Morse.1939} and used for the purposes of this work are indeed continuous.
    %
	Our \cref{def:critical_set} of a critical set $S$ of \emph{minimum type} also differs slightly from that of Morse and Tompkins \cite[p.~466]{Morse.1939}, who do not require the neighborhood $N$ of $S$ on which the function values exceed those on $S$ to contain the closure of $S$.
	Without this additional assumption, however, \cref{thm:mountain_pass} does not hold, as shown by the example $F \colon [0,1] \to \R$ with $F(0) = F(1) = 0$ and $F(t) = 1$ for $0 < t < 1$:
	$F$ has the four critical sets $\{0\}$, $\{1\}$, $\{0\} \cup \{1\}$ and $(0,1)$, which all satisfy the minimum type condition if the neighborhood $N$ need not contain their closure, but then there is no critical set that is not of minimum type.
\end{rem}

@@

\begin{lem}
\label{lem:essential_cech_dim}
	Let $F \colon M \to \R$ be a function on a connected non-empty metric space with compact sublevel set filtration such that the natural map $\colim \CH_0(F_{\leq \bullet}) \to \CH_0(M)$ is an isomorphism and $\CH_0(F_{\leq \bullet})$ is q-tame.
	Then the essential dimension of $\CH_0(F_{\leq \bullet})$ satisfies $\cp_{0} = 1$.
\end{lem}
\begin{proof}
	Since $M$ is connected and non-empty, we have $\dim H_{0}(M) = 1$ for singular homology, and since $M$ is non-empty we have $\dim \CH_0(M) \geq 1$.
	Now the natural map from singular to \v{C}ech homology is always surjective for compact metric spaces in dimension 0 \cite{Eda.2000}, so the map $H_{0}(F_{\leq t}) \to \CH(F_{\leq t})$ is surjective for all $t$.
	Hence, the morphism $H_{0}(F_{\leq \bullet}) \to \CH_{0}(F_{\leq \bullet})$ of persistence modules is epi.
	Taking colimits preserves epis, so the natural map $\colim H_{0}(F_{\leq \bullet}) \to \colim \CH_{0}(F_{\leq \bullet})$ is still epi. 
	We assume $\colim \CH_0(F_{\leq \bullet}) \to \CH_0(M)$ to be an isomorphism, so the composition $\colim H_0(F_{\leq \bullet}) \to \CH_0(M)$ is still epi.
	But this map factors through $H_{0}(M)$, which has dimension 1, so we get $\dim \CH_0(M) = 1$.
	Together with our assumption that $\colim \CH_{0}(F_{\leq \bullet}) \cong \CH_{0}(M)$, we obtain $\cp_0 = \dim \colim \CH_0(F_{\leq \bullet}) = \dim \CH_0(M) = 1$.
\end{proof}

>>>>

\begin{rem}\label{rem:critical_set}
    %Our \cref{def:critical_set} of homotopically regular point differs slightly from that of \citet[p.~30]{Morse.1938} and \citet[p.~444--445]{Morse.1939} as their displacement functions are not explicitly assumed to be continuous.
    %As used in the proof of \cref{thm:sublevel_set_homotopy}, we require this property to establish that a homotopically regular point with value $t$ admits a neighborhood $U$ and a homotopy $\varphi$ as in \cref{def:critical_set} such that for any compact $V \subseteq U$ there is $\epsilon > 0$ with $\varphi(V, 1) \subseteq F_{\leq t - \epsilon}$.
    %That such neighborhoods exist is claimed by Morse in the proof of \cite[Lemma~8.1]{Morse.1938}, where continuity of the displacement functions is not mentioned explicitly.
    %It is not clear to us whether the claim actually holds without continuity, or whether the assumption of continuity was made implicitly.
    %Regardless, all displacement functions considered by \citet{Morse.1939} and used for the purposes of this work are indeed continuous.
    %
	Our \cref{def:critical_set} of a critical set $S$ of \emph{minimum type} differs slightly from that of Morse and Tompkins \cite[p.~466]{Morse.1939}, who do not require the neighborhood $N$ of $S$ on which the function values exceed those on $S$ to contain the closure of $S$.
	Without this additional assumption, however, \cref{thm:mountain_pass} does not hold, as shown by the example $F \colon [0,1] \to \R$ with $F(0) = F(1) = 0$ and $F(t) = 1$ for $0 < t < 1$:
	$F$ has the four critical sets $\{0\}$, $\{1\}$, $\{0\} \cup \{1\}$ and $(0,1)$, which all satisfy the minimum type condition if the neighborhood $N$ need not contain their closure, but then there is no critical set that is not of minimum type.
\end{rem}

@@

\begin{lem}
\label{lem:essential_cech_dim}
	Let $F \colon M \to \R$ be a function on a connected non-empty metric space with compact sublevel set filtration such that the natural map $\colim \CH_0(F_{\leq \bullet}) \to \CH_0(M)$ is an isomorphism and $\CH_0(F_{\leq \bullet})$ is q-tame.
	Then the essential dimension of $\CH_0(F_{\leq \bullet})$ satisfies $\cp_{0} = 1$.
\end{lem}
\begin{proof}
	Since $M$ is connected and non-empty, we have $\dim H_{0}(M) = 1$ for singular homology, and since $M$ is non-empty we have $\dim \CH_0(M) \geq 1$.
	Now the natural map from singular to \v{C}ech homology is always surjective for compact metric spaces in dimension 0 \cite{Eda.2000}, so the map $H_{0}(F_{\leq t}) \to \CH_0(F_{\leq t})$ is surjective for all $t$.
	Hence, the morphism $H_{0}(F_{\leq \bullet}) \to \CH_{0}(F_{\leq \bullet})$ of persistence modules is epi.
	Taking colimits preserves epis, so the natural map $\colim H_{0}(F_{\leq \bullet}) \to \colim \CH_{0}(F_{\leq \bullet})$ is still epi.
	We assume $\colim \CH_0(F_{\leq \bullet}) \to \CH_0(M)$ to be an isomorphism, so the composition $\colim H_0(F_{\leq \bullet}) \to \CH_0(M)$ is still epi.
	But this map factors through $H_{0}(M)$, which has dimension 1, so we get $\dim \CH_0(M) = 1$.
	Together with our assumption that $\colim \CH_{0}(F_{\leq \bullet}) \cong \CH_{0}(M)$, we obtain $\cp_0 = \dim \colim \CH_0(F_{\leq \bullet}) = \dim \CH_0(M) = 1$.
\end{proof}
